\thesistitle

### 2019-07-23 sections/research.tex
Better type 2 example

	public void addTen(int x) {
|\highlightYellow|		x = x + 10;
|\highlightYellow|		ChangeNotifier.notifyChanged(x);
|\highlightYellow|		return x;
	}
}
\end{javacode}}
\colchunk[2]{
\begin{javacode}
package com.sb.fruitgame;

@@

	public void concatTen(String x) {
|\highlightYellow|		x = x + 10;
|\highlightYellow|		ChangeNotifier.notifyChanged(x);
|\highlightYellow|		return x;
	}
}
\end{javacode}}
\end{parcolumns}
\caption{Variables with different types but the same name.}
\label{fig:type2variables}
\end{figure}
\begin{figure}[H]
  \includegraphics[width=1\columnwidth]{img/type1}
  \caption{Example of a type 1 clone that is functionally different.}
  \label{fig:type1}
\end{figure}

@@

\begin{figure}[H]
  \includegraphics[width=1\columnwidth]{img/type2}
  \caption{Example of a type 2 clone.}
  \label{fig:type2}
\end{figure}

The example in figure \ref{fig:type2} shows a type 2 clone that poses no harm to the design of the system. Both methods are, except for their matching structure, completely different in functionality. They operate on different types, call different methods, return different things, etc. Having such a method flagged as a clone does not provide much useful information.

>>>>

	public void addTen(int x) {
|\highlightYellow|		x = x + 10;
|\highlightYellow|		Notifier.notifyChanged(x);
|\highlightYellow|		return x;
	}
}
\end{javacode}}
\colchunk[2]{
\begin{javacode}
package com.sb.fruitgame;

@@

	public void concatTen(String x) {
|\highlightYellow|		x = x + 10;
|\highlightYellow|		Notifier.notifyChanged(x);
|\highlightYellow|		return x;
	}
}
\end{javacode}}
\end{parcolumns}
\caption{Example of a type 1 clone that is functionally different.}
\label{fig:type1}
\end{figure}

@@

\begin{figure}[H]
\begin{parcolumns}{2}
\colchunk[1]{
\begin{javacode}
|\highlightYellow|public boolean redCircles
|\highlightYellow|          (List<Circle> circles){
|\highlightYellow|	return circles.stream()
|\highlightYellow|           .allMatch(Shape::isRed);
|\highlightYellow|}
\end{javacode}}
\colchunk[2]{
\begin{javacode}
|\highlightYellow|public Apple getEdibleApple
|\highlightYellow|         (Basket<Apple> basket){
|\highlightYellow|	return basket.getFruit()
|\highlightYellow|        .getApple(Fruit::notEaten);
|\highlightYellow|}
\end{javacode}}
\end{parcolumns}
\caption{Example of a type 2 clone with high variability between fragments.}
\label{fig:type2}
\end{figure}

The example in figure \ref{fig:type2} shows a type 2 clone class. Both methods are, except for their matching structure, completely different in functionality. They operate on different types, call different methods, return different things, etc. Having such a method flagged as a clone does not provide much useful information.
